\section{Related Work}
\label{sec:related_work}

\method{} sits at the intersection of text-to-image generation, visual
grounding, interactive visualization, and LLM answer presentation. As the task
of turning an LLM answer into a region-interactive visual image is, to our
knowledge, new, we review the closest adjacent lines and the gap \method{} fills.

\paragraph{Text-to-image and controllable generation.}
Diffusion models~\citep{ramesh2022dalle2,saharia2022imagen,rombach2022ldm,podell2024sdxl}
produce high-fidelity images but do not follow spatial instructions precisely:
``place module~A top-left'' yields no guarantee~\citep{feng2023layoutgpt,cheng2024intelligent}.
Controllable methods such as ControlNet~\citep{zhang2023controlnet},
GLIGEN~\citep{li2023gligen}, training-free
layout-to-image~\citep{chen2024trainingfree},
and InfographicNLP~\citep{lu2023infographicnlp} impose structure but target
synthesis quality, not making generated regions \emph{interactive} and
\emph{aligned with a structured answer}. \method{} uses text-to-image as a
rendering backend but does not rely on its layout fidelity: it discovers
region locations \emph{after} generation via grounding.

\paragraph{Visual grounding and segmentation.}
\begin{sloppypar}
Referring localization methods such as MDETR~\citep{kamath2021mdetr},
TransVG~\citep{deng2021transvg}, UNINEXT~\citep{yan2023uninext}, Grounding
DINO~\citep{liu2024groundingdino}, and YOLO-World~\citep{cheng2024yoloworld},
as well as
grounding-oriented VLMs~\citep{nvidia2025locateanything,xiaomi2025mimovl,liu2023llava,chen2024internvl}
output boxes for descriptive prompts; SAM/SAM2~\citep{kirillov2023sam,ravi2024sam2}
refine a box into a mask. \method{} repurposes this family for a new goal: not
finding a pre-existing object, but \emph{aligning a structured answer's regions
to their actual rendered positions} in a freshly generated image.
\end{sloppypar}

\paragraph{Interactive visualization, VQA, and structured LLM output.}
Interactive image annotation~\citep{hochheiser2004interactive,munzner2014visualization}
and VQA~\citep{antol2015vqa,goyal2017vqav2,mathew2021docvqa,masry2022chartqa}
explore \emph{fixed} images rather than answer-generated ones, and VQA treats
the image as input to be queried, not as an \emph{answer} to be navigated.
Structured-output work such as chain-of-thought~\citep{wei2022cot},
ReAct~\citep{yao2023react}, tool use~\citep{schick2023toolformer},
and RAG~\citep{lewis2020rag,gao2024ragsurvey} structures \emph{reasoning}, not
the output \emph{modality}; the answer stays text. Mind-map and
chart-generation methods~\citep{zhang2014mindmap,hu2024llmmindmap,obeid2020charttotext,tang2023chartlama}
visualize structure but as static outputs without image-level region interaction
or grounding. \method{} combines these threads into a new task: an LLM answer
rendered as a navigable, region-interactive visual image with vision-grounded
hotspots, for which we provide an open-source system, benchmark, and evaluation.
